%====================
% EXPERIENCE A
%====================
\subsection{{Data Scientist \hfill 08-2022 $-$ Present}}
\subtext{King (previously Activision/Bizzard, now part of Microsfot Xbox Games) \hfill London - United Kingdom}
\begin{zitemize}
\item Collaborated with cross-functional teams, including the in-app purchases team, to design and execute tests, enhancing the understanding of user preferences regarding pricing options for virtual products in ``Candy Crush Saga'' (CCS).
\item Developed a collaborative filtering recommender system to personalize product placements based on historical purchase data (implicit feedback), impacting user engagement, product discovery and revenue potential in CCS.
\item Contributed directly to one of our game feature simulators by adding new features to the code and introduced an enhanced configuration that, once implemented in the live production environment, resulted in  $\approx0.6\%$ uplift in revenue.
\item Played a key role in designing A/B testing specifications and custom tracking events for client apps, enabling the rigorous evaluation of new game features and directly influencing game development decisions in ``Bubble Witch 3 Saga'' (BW3S).
\item Led data-driven analysis across BW3S and CCS game teams, crafting and delivering key reports on metrics such as daily active users, gross revenue, ad revenue, daily paying users, and player interaction to stakeholders.
\item Provided several big data analysis using SQL (GCP Big Query) and Python to track app events, which involved evaluating completion rates and engaging players with new game features and events.
\item Authored Python-based data analytics tools, encompassing data visualization, ETL processes, feature simulation, and forecasting, to support business performance and product analytics functions (e.g. game feature simulation improvements, uplift forecasting panels, model error dashboard analysis and MDE calculator).
\item Enhanced software development practices by integrating continuous integration, rigorous unit testing with Pytest, thorough code reviews, and robust version control practices maintaining high-quality code standards.
\end{zitemize}


%====================
% EXPERIENCE B
%====================
\subsection{{Data Scientist / Marketing Analytics \hfill 08-2021 $-$ 07-2022}}
\subtext{Magazine Luiza (one of the largest retailers in Brazil) \hfill São Paulo, SP - Brazil}
\begin{zitemize}
\item Automated the maintenance and provided intraday insights for smart shopping campaigns via the Google Ads API, delivering critical business intelligence to the Marketing team and supporting real-time evaluation of marketing metrics.
\item Designed and deployed rule-based models to streamline shopping campaign performance by assessing product viability through historical ad spend and ROI data, successfully reducing ad waste and optimizing cash margin.
\item Conducted a comprehensive analysis of seller performance within the marketplace to determine regional conversion rates, revealing a correlation between conversion rates and customer proximity. This insight led to initiatives of strategic limitation of ad impressions for small sellers aiming for boosting investment efficiency, overall conversion rates, and local delivery performance.
\item Played a pivotal role in the Advanced Analytics team, leveraging data to enhance operations across logistics, supply chain, and marketing. 
\item Expertly manipulated large datasets using Airflow, PySpark and maintained sophisticated SQL queries with BigQuery, enhancing data processing and operational efficiency.
\item Fostered a collaborative environment through continuous engagement with the Data Engineering team, significantly improving the deployment process and performance of analytics products. 
\item Maintained high code quality and traceability using Gitlab for version control.
\item Delivered actionable insights and strategic reports to executive leadership and operational stakeholders, driving data-centric decisions and advancing the progress of key analytical initiatives.
\end{zitemize}


%====================
% EXPERIENCE C
%====================
\subsection{{Data Science Instructor \hfill 03-2022 $-$ 06-2022}}
\subtext{Ultima School \hfill São Paulo, SP - Brazil}
\begin{zitemize}
\item I have developed instructional material (videos and tutorials) for basic Python programming, Python development interfaces (such as Jupyter Notebooks, VS Code and Google Colab) 
and basic statistics for data science beginners.
\item I recorded live webinars with students using a code-along approach to demonstrate all the basic tools of Python programming and basic concepts of statistics.
\item I have written the Data Processing module material with 4 chapters focusing on all the basic tools of the pandas library. My material contains practical examples 
and exercises using an open dataset of Brazilian E-commerce from Olist, available in Kaggle. I also recorded webinars with the students solving exercises 
and showing how to use pandas operations and table manipulation.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Assistant Professor \hfill 03-2017 $-$ 08-2021}}
\subtext{Instituto Federal Sul-rio-grandense (IFSul) \hfill Sapiranga, RS - Brazil}
\begin{zitemize}
\item Lectured on a diverse range of technical courses, significantly contributing to the education of future professionals in Electromechanics, Electro-electronics, and Electrotechnics. 
\item Produced and disseminated educational content, amassing substantial views on the institution's YouTube page, enhancing the program's visibility and student engagement.
\item Mentored and advised students in executing high-caliber research projects, leading to successful project conclusions and presentations. Notable projects included developing a photovoltaic panel-powered USB charger, creating a machine learning algorithm to detect depression symptoms in Twitter users, and implementing a facial detection system for mask usage during the COVID-19 pandemic.
\item Successfully managed project timelines, resources, and student assignments, ensuring projects were delivered on time and with high quality, fostering an environment of excellence and innovation.
\item Coordinated a student music group and produced video training materials on G-Suite tools, demonstrating strong leadership and project management skills beyond the classroom.
\item Actively participated in and contributed to internal events and committees, showcasing commitment to institutional service and community engagement, and strengthening interdisciplinary collaboration.
\item Collaborated with scientific research and paper publications while co-adivising master students of other institutions in research projects.
\end{zitemize}



%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
