%====================
% Objective Statement
%====================


%\blindtext[1]

% INTRO AND ABOUT ME
As a seasoned data scientist with years of in-depth industry experience and an extensive background in academia, 
I bring a unique blend of technical expertise, strategic thinking, and leadership skills to the table. 
I have a profound passion for leveraging technology, data analytics, and mathematical modeling 
to unravel complex business challenges and drive impactful decisions.
%
% MY EXPERIENCE
In my journey through academia as an assistant professor, 
I honed my abilities in research, complex problem-solving, and project management, 
which I seamlessly transitioned into the industry sphere. 
My graduate work in digital signal processing and stochastic processes laid the groundwork for a deep understanding of analytical models, 
enabling me to specialize in and innovate upon data-driven strategies.
%
% JOB EXPERIENCES
During my tenure at King, a prominent player in the mobile gaming industry, 
I have worked on multiple projects with relevant impact on the business, including: 
in-apps purchase analysis and product placement personalization with recommender systems, 
the design and implementation of analytics tools that drive game feature optimization, 
the strategic planning and evaluation of A/B tests that measure player engagement and revenue growth. 
These initiatives have not only enhanced game performance but have also contributed to significant business growth.
%
In my previous experiences, I have also contributed significantly to the success of my employers and teams.
In marketing analytics at a leading Brazilian e-commerce platform, 
I was able to automate and refine data processes while managing stakeholders expectations and demands,
directly boosting performance metrics for shopping ads. 
Throughout, my previous career path as a professor and researcher has fortified my leadership capabilities, 
allowing me to effectively communicate complex concepts, mentor emerging talent, and manage diverse teams.
%
% G0ALS
I am now eager to elevate my career to a senior data science role where I can further influence business strategy, 
foster a culture of data-centric innovation, and lead teams to break new ground in driving business success.
I am particularly interested in opportunities involving monetization optimization, business growth and strategic plan, personalization and recommender systems. 